---
editor_options:
  chunk_output_type: console
---

# INTERNAL

## Avoid `R CMD check` notes about undefined global objects used in magrittr pipes

cf. <https://github.com/tidyverse/magrittr/issues/29#issuecomment-74313262>

```{r}
utils::globalVariables(names = c(".",
                                 "cached",
                                 "id",
                                 "name"))
```

# `register`

```{r}
#' Register a package's user-cache pins board
#'
#' This function registers a package's user-cache pins board. It will be automatically called when needed.
#'
#' @inheritParams boardname
#'
#' @return `boardname` invisibly if it wasn't registered before, otherwise `NULL`.
#' @export
#'
#' @examples
#' \dontrun{
#' # you could register the cache on package load, although this is not necessary in most cases
#' .onLoad <- function(libname, pkgname) {
#'   pkgpins::register(pkgname)
#' }}
register <- function(pkg) {
  
  if (!(boardname(pkg) %in% pins::board_list())) {
    
    pins::board_register_local(name = boardname(pkg),
                               cache = pins::board_cache_path(),
                               versions = FALSE)
  }
}
```

# `deregister`

```{r}
#' Deregister a package's user-cache pins board
#'
#' This function deregisters a package's user-cache pins board.
#'
#' Ideally, you call this function on [package unload][base::.onUnload]. See the examples for details.
#'
#' @inheritParams boardname
#'
#' @return `NULL`.
#' @export
#'
#' @examples
#' \dontrun{
#' # deregister the cache on package unload (recommended)
#' .onUnload <- function(libpath) {
#'   pkgpins::deregister()
#' }}
deregister <- function(pkg) {
  
  if (boardname(pkg) %in% pins::board_list()) {
    
    pins::board_deregister(name = boardname(pkg))
  }
}
```

# `boardname`

By convention, the pins board name is identical to the directory name.

```{r}
#' Get a package's user-cache pins board name
#'
#' This function returns the board name of the `pks`'s user-cache pins board. 
#' 
#' It shouldn't be necessary to rely on this function for the tasks this package is intended to perform, though.
#'
#' @param pkg Package name. A character scalar.
#'
#' @return The board name of the [user-cache pins board](https://pins.rstudio.com/articles/boards-understanding.html) belonging to `pkg`, which is at the same
#'   time the name of the filesystem directory beneath [pkgpins::path_cache()]. A character scalar.
#' @export
#'
#' @examples
#' \donttest{
#' pkgpins::boardname(pkg = "not.a.real.pkg")}
boardname <- function(pkg) {
  
  paste0("pkg-cache-", checkmate::assert_string(pkg))
}
```

# `path_cache`

```{r}
#' Get a package's user-cache pins board path
#'
#' This function allows to the determine the filesystem path to the `pkg`'s user-cache pins board. Note that this path depends on the operating system this
#' function is called from.
#' 
#' It shouldn't be necessary to rely on this function for the tasks this package is intended to perform, though.
#'
#' @inheritParams boardname
#'
#' @return A path of type [fs_path][fs::path()].
#' @export
#'
#' @examples
#' \donttest{
#' pkgpins::path_cache(pkg = "not.a.real.pkg")}
path_cache <- function(pkg) {
  
  fs::path(pins::board_cache_path(), boardname(pkg))
}
```

# `ls_cache`

```{r}
#' List all objects in a package's user-cache pins board
#'
#' This function lists all object `id`s belonging to a `pkg`'s user-cache pins board, together with the date and time they were `cached`.
#'
#' @inheritParams boardname
#'
#' @return A [tibble][tibble::tbl_df].
#' @export
#'
#' @examples
#' \donttest{
#' pkgpins::ls_cache(pkg = "not.a.real.pkg")}
ls_cache <- function(pkg) {
  
  register(pkg = pkg)
  result <- pins::pin_find(board = boardname(pkg),
                           extended = TRUE)
  
  if ("cached" %in% colnames(result)) {
    result %<>% dplyr::transmute(id = name,
                                 cached = lubridate::as_datetime(cached,
                                                                 tz = "UTC"))
  } else {
    result <- tibble::tibble(id = character(),
                             cached = lubridate::as_datetime(integer(),
                                                             tz = "UTC"))
  }
  
  result
}
```

# `clear`

```{r}
#' Delete all objects from a package's user-cache pins board exceeding a certain age
#'
#' This function allows to clean up old caching left-overs. It could be called on package load/unload, for example.
#'
#' @inheritParams boardname
#' @param max_age The age above which cached objects will be deleted. A valid [lubridate duration][lubridate::as.duration]. Defaults to 1 day (24 hours).
#'
#' @return The IDs of the deleted objects invisibly.
#' @export
#'
#' @examples
#' \dontrun{
#' # delete all cached results that are older than 7 days at once on package load:
#' .onLoad <- function(libname, pkgname) {
#'   pkgpins::clear(pkg = pkgname,
#'                  max_age = "7 days")
#' }}
clear <- function(pkg,
                  max_age = "1 day") {
  
  register(pkg = pkg)
  
  ls_cache(pkg) %>%
    dplyr::filter(lubridate::now(tzone = "UTC") - cached > lubridate::as.duration(max_age)) %$%
    id %>%
    purrr::walk(.f = pins::pin_remove,
                board = boardname(pkg))
}
```

# `cache_obj`

**Notes:**

-   Pinning an object with `I()` as below [avoids the creation of a CSV copy](https://github.com/rstudio/pins/pull/74) which improves performance. The CSV is
    not needed by pkgpins anyway.

**TODO:**

-   [ ] Improve get performance by creating an in-memory copy and trying to retrieve it first before loading the on-disk copy. Ideally this functionality would
    be added to the underlying pins package, I guess.

    Another possibility would be to switch to the [storr](https://github.com/richfitz/storr) package which provides exactly this functionality. Additionally it
    might be worth to use the [thor](https://richfitz.github.io/thor/reference/storr_thor.html) package as the storr driver which provides an
    [LMDB](https://en.wikipedia.org/wiki/Lightning_Memory-Mapped_Database) interface which might prove faster than using serialized R data (`.rds`).

    See [here](https://richfitz.github.io/storr/articles/external.html#memoisation) for an experimental implementation of memoisation using the storr package.

```{r}
#' Cache an object to a package's user-cache pins board
#'
#' This function stores an object in a package's user-cache pins board.
#' 
#' The exact date and time (UTC) of the pinning is stored as the additional metadata `cached` which is of type [integer][base::integer]. You can restore the
#' actual datetime using [`lubridate::as_datetime(cached, tz = "UTC")`][lubridate::as_datetime] (note that [pkgpins::ls_cache()] does this automatically).
#'
#' See [pkgpins::call_to_hash()] for a convenient way to create an `id` that uniquely identifies a function call. Or just use [with_cache()].
#'
#' @inheritParams boardname
#' @param x An object, local file or remote URL to be cached.
#' @param id The pin name uniquely identifying `x` in the `pkg`'s user-cache pins board. A character scalar. Necessary to retrieve `x` again using
#'   [pkgpins::get_obj()]. An already existing pin named `id` will be silently overwritten.
#'
#' @return `x` invisibly.
#' @export
#'
#' @examples
#' \donttest{
#' library(magrittr)
#'
#' # if the fn below would be part of a real package, we could instead define `this_pkg`
#' # globally using `this_pkg <- utils::packageName()`
#' this_pkg <- "not.a.real.pkg"
#' 
#' # let's define a fn that returns R pkg sys deps from cache
#' pkg_sys_deps <- function(pkg,
#'                          use_cache = TRUE,
#'                          cache_lifespan = "6h") {
#'   fetch <- TRUE
#'
#'   if (use_cache) {
#'     pin_name <- pkgpins::call_to_hash()
#'     result <- pkgpins::get_obj(id = pin_name,
#'                                max_age = cache_lifespan,
#'                                pkg = this_pkg)
#'     fetch <- is.null(result)
#'       
#'   }
#'   
#'   if (fetch) {
#'     result <-
#'       jsonlite::fromJSON(txt = paste0("https://sysreqs.r-hub.io/pkg/", pkg),
#'                          simplifyVector = FALSE) %>%
#'       purrr::flatten()
#'   }
#'  
#'   if (use_cache && fetch) {
#'     pkgpins::cache_obj(x = result,
#'                        id = pin_name,
#'                        pkg = this_pkg)
#'   }
#'
#'   result
#' }
#'
#' # now get the sys deps for git2r for the first time (populating the cache)
#' pkg_sys_deps("git2r")}
#' \dontrun{
#' # for the `cache_lifespan` (we've set a default of 6h), the cached result will be returned
#' # (as long as `use_cache = TRUE`):
#' bench::mark("with cache" = pkg_sys_deps("git2r"),
#'             "without cache" = pkg_sys_deps("git2r", use_cache = FALSE),
#'             iterations = 10,
#'             relative = TRUE)}
cache_obj <- function(x,
                      id,
                      pkg) {
  
  checkmate::assert_string(id)
  register(pkg = pkg)
  
  pins::pin(x = I(x),
            board = boardname(pkg),
            name = id,
            metadata = list(cached = lubridate::now(tzone = "UTC")))
}
```

# `get_obj`

```{r}
#' Get a cached object from a package's user-cache pins board
#'
#' This function retrieves a cached object from a package's user-cache pins board _if_ it is not older than `max_age`.
#'
#' @inheritParams boardname
#' @param id The pin name uniquely identifying the object to be retrieved from the `pkg`'s user-cache pins board. A character scalar.
#' @param max_age The maximum age the cached object is allowed to have. A valid [lubridate duration][lubridate::as.duration]. Defaults to 1 day (24 hours).
#'
#' @return The cached object if it is not older than `max_age`, otherwise `NULL`.
#' @export
#'
#' @examples
#' \donttest{
#' pkgpins::get_obj(id = "something",
#'                  pkg = "some_pkg",
#'                  max_age = "2 weeks")}
get_obj <- function(id,
                    pkg,
                    max_age = "1 day") {
  
  checkmate::assert_string(id)
  register(pkg = pkg)
  board <- boardname(pkg)
  result <- pins::pin_find(name = id,
                           board = board,
                           extended = TRUE)
  
  if (nrow(result) > 1L) {
    rlang::abort(paste0("Multiple pins found for board '", board, "'!\nThis should not happen since versioning is disabled for pkgpins boards... \U1F41E"))
    
  } else if (nrow(result) == 1L) {
    
    if (!("cached" %in% colnames(result))) {
      rlang::abort(paste0("Corrupted package cache detected! Please delete the directory `", path_cache(pkg = pkg), "` and then try again."))
    }
    
    result %<>%
      dplyr::filter(lubridate::now(tzone = "UTC") - lubridate::as_datetime(cached, tz = "UTC") <= lubridate::as.duration(max_age)) %$%
      name
    
    if (length(result) > 0L) {
      result <- pins::pin_get(board = board,
                              name = id)
    } else{
      result <- NULL
    }
    
  } else {
    result <- NULL
  }
  
  result
}
```

# `rm_obj`

```{r}
#' Delete a cached object from a package's user-cache pins board
#'
#' Note that it normally won't be necessary to delete a cached object using this function because [pkgpins::cache_obj()] will always overwrite a possibly
#' existing object in the cache with the same `id`. If you want to ensure that no "data corpses" are left behind from using [pkgpins::cache_obj()], consider
#' clearing the whole package user-cache pins board at once using [pkgpins::clear()].
#'
#' @inheritParams boardname
#' @param id The pin name uniquely identifying the object to be deleted from the `pkg`'s user-cache pins board. A character scalar.
#'
#' @export
#'
#' @examples
#' \donttest{
#' pkgpins::rm_obj(id = "git2r-syreqs",
#'                 pkg = "not.a.real.pkg")}
rm_obj <- function(id,
                   pkg) {
  
  checkmate::assert_string(id)
  register(pkg = pkg)
  
  pins::pin_remove(board = boardname(pkg),
                   name = id)
}
```

# `call_to_hash`

TODO:

-   [ ] Fix the environment/frame issue!

    **THIS IS SERIOUS!** The `args` are not properly evaluated, i.e. the search path (or "env stack", "call stack", or whatever) is "cut off".

    Real-life example where this matters:

    ``` {.r}
    testf <- function(param) swissmuni::snapshots(historicized_code = param)
    testf(TRUE)

    # avoiding calling `call_to_hash()`
    testf <- function(param) swissmuni::snapshots(historicized_code = param, use_cache = FALSE)
    testf(TRUE)
    ```

    Or a simpler synthetic example:

    ``` {.r}
    foo <- function(add_ns) pkgpins::call_to_hash(add_namespace = add_ns)
    bar <- function(really_add_ns) foo(add_ns = really_add_ns)
    foo(TRUE)
    bar(TRUE)
    ```

    -   [x] Thoroughly read the chapter [Environments](https://adv-r.hadley.nz/environments.html), especially the subchapter [Call
        stacks](https://adv-r.hadley.nz/environments.html#call-stack), of the *Advanced R* book to better understand the whole situation.

    NOTES:

    -   As it appears, the current way is likely a dead end because we seem to "break" R's concept of
        [promises](https://adv-r.hadley.nz/functions.html#promises) (see also the [official
        doc](https://cran.r-project.org/doc/manuals/r-release/R-lang.html#Promise-objects)) by trying to reconstruct the args from `match.call()`... (is this
        really true, i.e. there's no way to get the args as the original *promises* instead of just symbols?)

        We could try to work around this by iteratively calling `rlang::env_has(env = parent.frame(n), nms = arg, inherit = TRUE)` with an incresing `n` until
        it returns TRUE, but this would obviously be bad since it's not guaranteed that we find the right `arg` object.

        Or would simply requiring the calling env as an argument to `call_to_hash()` help? No. Really, nope!

    -   *Quosures* might provide a way out -\> thoroughly read the whole [part IV (Metaprogramming)](https://adv-r.hadley.nz/metaprogramming.html) of the
        *Advanced R* book!

-   [ ] Make sure implicit default arguments are also hashed; currently hashing `fn()` and `fn(defaults)` results in different hashes which is inconvenient.

-   [ ] Add a param `add_pkg_version` (default `TRUE`) to add the package version the namespace belongs to to the hash. Only relevant if `add_namespace = TRUE`.

    This would allow for breaking changes in e.g. dataset schema of `c2d::referendums()` without the need for the user to `clear()` the pkg cache as long as the
    pkg version is updated with the breaking changes!

-   [ ] Switch from `digest::digest(algo = "xxhash64")` to [`rlang::hash()`](https://rlang.r-lib.org/reference/hash.html)?

    Possible contra: The latter is a xxHash 128-bit digest instead of a 64-bit one -\> wasted space?

    Pro: We could drop the *digest* dependency.

```{r}
#' Convert the calling function call to a hash
#'
#' Creates a string that uniquely identifies the function call of the calling function by the function's namespace, name and a hash of the specified arguments.
#' For example, when called _inside_ the function `foo()`, it will return
#' `r foo <- function(a, b, c) call_to_hash(); pal::prose_ls(foo(a = F, b = "bar", c = 1), wrap = '"')` when `foo()` was called with
#' `foo(a = F, b = "bar", c = 1)`.
#' 
#' This function does evaluate object names passed as function arguments. I.e. the function call `foo(a = my_var)` will result in
#' `r my_var <- 100; pal::prose_ls(foo(100), wrap = '"')` if `my_var`'s value is `100`, whereas it will become
#' `r my_var <- 101; pal::prose_ls(foo(101), wrap = '"')` if `my_var`'s value is `101`.
#'
#' @param n_generations_back The number of generations to go back. See [sys.parent()] for details. An integerish scalar.
#' @param add_namespace Whether to prefix the generated string with the [namespace](https://cran.r-project.org/doc/manuals/r-release/R-ints.html#Namespaces)
#'   (i.e. package name) the called function belongs to (if any).
#' @param exclude_args Argument names to be ignored, i.e. excluded from the generated string. A character vector, or `NULL` for no excluded arguments.
#'
#' @return A character scalar.
#' @export
#'
#' @examples
#' # By default, the parent function call is returned ...
#' foo <- function(a, b, c) pkgpins::call_to_hash()
#' foo("ya", "hoo")
#'
#' # ... but you can go back further and return e.g. the grandparent function call
#' foo <- function(a) pkgpins::call_to_hash(n_generations_back = 2L)
#' bar <- function(b) foo()
#' bar()
#'
#' # Arguments can be excluded by name ...
#' foo <- function(x, y, z) pkgpins::call_to_hash(exclude_args = c("x", "z"))
#' # ... thus the following three calls will all result in the same hash
#' foo(1+1, 'ar', list('1,77'))
#' foo(y = 'ar', list('1,77'))
#' foo(, "ar",)
call_to_hash <- function(n_generations_back = 1L,
                         add_namespace = TRUE,
                         exclude_args = c("use_cache", "cache_lifespan")) {
  
  checkmate::assert_count(n_generations_back)
  checkmate::assert_flag(add_namespace)
  checkmate::assert_character(exclude_args,
                              any.missing = FALSE,
                              null.ok = TRUE)
  
  parent_frame_nr <- sys.parent(n_generations_back)
  parent_frame <- sys.frame(parent_frame_nr)
  call <- match.call(definition = sys.function(parent_frame_nr),
                     call = sys.call(parent_frame_nr))
  fn_name <- as.character(as.list(call)[[1L]])
  args <- as.list(call[-1L])
  
  # add namespace
  ## extract it if provided in call
  if (length(fn_name) == 3L) {
    
    fn_namespace <- fn_name[2L]
    fn_name <- fn_name[3L]
    
    ## or otherwise determine it manually
  } else if (length(fn_name) == 1L) {
    
    fn_envs <- methods::findFunction(f = fn_name,
                                     where = parent_frame)
    
    ### reduce to the first visible version of the function and extract env and namespace name
    if (length(fn_envs)) {
      
      fn_namespace <-
        fn_envs %>%
        dplyr::first() %>%
        environmentName() %>%
        ### reduce to actual package _namespace_ (in contrast to _environment_, cf. https://stackoverflow.com/a/38872833/7196903)
        stringr::str_extract(pattern = "(?<=^package:).+")
      
    } else {
      fn_namespace <- NA_character_
    }
  } else {
    rlang::abort("Unknown situation detected: Call's function has a length of 2! Please debug...")
  }
  
  if (add_namespace && !is.na(fn_namespace)) {
    fn_name %<>% paste0(fn_namespace, "-", .)
  }
  
  # add args
  if (!is.null(exclude_args)) {
    excl <- names(args) %in% exclude_args
    
    if (length(excl)) {
      args <- args[!excl]
    }
  }
  
  if (length(args) > 0L) {
    
    # evaluate the call's arguments in the calling environment
    result <-
      args %>%
      purrr::map(.f = eval,
                 envir = parent_frame) %>%
      expr_to_hash() %>%
      paste0(fn_name, "-", .)
      
  } else {
    result <- fn_name
  }
  
  result
}

expr_to_hash <- function(expr) {
  
  digest::digest(object = expr,
                 algo = "xxhash64",
                 serializeVersion = 3L)
}

# these are necessary for testing the `add_namespace` argument
test_call_to_hash <- function(...) call_to_hash()
test_call_to_hash_no_ns <- function(...) call_to_hash(add_namespace = FALSE)
```

# `call_to_name`

**Notes:**

-   This function is deprecated, use `call_to_hash()` instead.

    The reason is that the path sanitization (`sanitize = TRUE`) using `fs::path_sanitize()` cuts of the name at a maximum of 255 chars which is the maximum for
    [most FS'](https://en.wikipedia.org/wiki/Comparison_of_file_systems#Limits). And anyway, it was stupid to not use hashing in the first place. 🙄

-   The following seemingly weird behaviour is not a bug of `call_to_name()`:

    ``` {.r}
    foo <- function(x, c) call_to_name(exclude_args = c("some_inexistent_arg_name"))
    # as long as arg `c` is provided, R doesn't care about missing args
    foo(, 1)
    # otherwise, R suddenly complains about missing `c`!
    foo()
    foo(1)
    ```

    While inspecting the function with `browser()`, I've observed that the error occurs as soon as `exclude_args` is accessed. But as it seems, an error only
    occurs if

    -   one of `foo()`'s params is named `c`
    -   `exclude_args` (or any other param in fact) is set to `c(...)`

    My best guess is that it has something to do with R's lazy evaluation; because the function `c()` and the variable/param `c` share names/symbols, R has to
    disambiguate them; accessing the param with the `c(...)` value thus also triggers an evaluation of the param named `c` (since it's found in the current
    env); no name clashes, no lazy eval.

    An easy prove that the issue is not specific to `call_to_name()`:

    ``` {.r}
    foo <- function(x, c) c(1,2)
    foo(, 1)
    foo(1)
    foo()
    ```

```{r}
#' Convert the calling function call to a name
#'
#' @description
#'
#' `r lifecycle::badge("deprecated")`
#'
#' _It's recommended to switch to the more reliable/powerful alternative [call_to_hash()] whenever possible._
#'
#' Strives to create a string that uniquely identifies the function call of the calling function by the function's namespace, name and specified arguments. For
#' example, when called _inside_ the function `foo()`, it will return
#' `r foo <- function(a, b, c) call_to_name(); pal::prose_ls(foo(a = F, b = "bar", c = 1), wrap = '"')` when `foo()` was called with
#' `foo(a = F, b = "bar", c = 1)`.
#'
#' @details
#' 
#' This function does evaluate object names passed as function arguments. I.e. the function call `foo(a = my_var)`, where `my_var`'s value is `100`, will be
#' converted to `r my_var <- 100; pal::prose_ls(foo(100), wrap = '"')`.
#' 
#' Nevertheless, it should be used with caution since the name conversion can be destructive: For instance, whitespaces are just deleted, thus
#' `foo(a = "ho ho")` and `foo(a = paste("ho", "ho", sep = paste0(rep(" ", 5), collapse = "")))` both produce the name
#' `r pal::prose_ls(foo(a = paste("ho", "ho", sep = paste0(rep(" ", 5), collapse = ""))), wrap = '"')` by default. Set `rm_blanks = FALSE` in order to keep
#' whitespaces.
#' 
#' Also, characters which are problematic or have special meaning on common filesystems are removed by default. To prevent this, use `sanitize = FALSE`
#' instead.
#' 
#' To turn off all the known-to-be destructive conversion steps at once, set `non_destructive = TRUE`.
#'
#' A more reliable/powerful alternative to this function is [call_to_hash()] which should be preferred whenever possible.
#'
#' @param rm_blanks Remove all whitespaces from `call`'s evaluated argument names.
#' @param sanitize Remove characters which are problematic or have special meaning on common filesystems from `call`'s evaluated argument names. Enabled by
#'   default. See [fs::path_sanitize()] for details about the performed sanitation.
#' @param non_destructive Disable all name conversion steps which are known to be destructive (loss of information). See details. This setting implies
#'   `santize = FALSE` and `rm_blanks = FALSE` and has precedence over them.
#' @param warn_incomplete Show a warning if the deparser _suspects_ it's unable to properly deparse an argument (might involve false positives). See the
#'   `"warnIncomplete"` section in [`base::..deparseOpts`][base::..deparseOpts] for details. A logical scalar.
#' @inheritParams call_to_hash
#'
#' @return A character scalar.
#' @export
#'
#' @examples
#' # By default, the parent function call is returned ...
#' foo <- function(a, b, c) pkgpins::call_to_name()
#' foo("ya", "hoo")
#'
#' # ... but you can go back further and return e.g. the grandparent function call
#' foo <- function(a) pkgpins::call_to_name(n_generations_back = 2L)
#' bar <- function(b) foo()
#' bar()
#'
#' # Whitespaces are removed by default
#' # which means the following produces identical names ...
#' foo <- function(a, b, c) pkgpins::call_to_name()
#' foo(4 - 2, 'a \" r', list("1, 77"))
#' foo(1+1, 'ar', list('1,77'))
#' 
#' # ... to avoid this and produce distinct names instead, set `rm_blanks = FALSE` ...
#' foo <- function(a, b, c) pkgpins::call_to_name(rm_blanks = FALSE)
#' foo(4 - 2, 'a \" r', list("1, 77"))
#' foo(1+1, 'ar', list('1,77'))
#' 
#' # ... or just disable the known to be destructive conversion steps altogether
#' foo <- function(a, b, c) pkgpins::call_to_name(non_destructive = TRUE)
#' foo(4 - 2, 'a \" r', list("1, 77"))
#' foo(1+1, 'ar', list('1,77'))
#'
#' # Arguments can be excluded by name
#' foo <- function(a, b, c) pkgpins::call_to_name(exclude_args = c("a", "c"))
#' foo(1+1, 'ar', list('1,77'))
#'
#' \dontrun{
#' # R's deparsing warns about possible incompletion when arguments are
#' # formulas or curly-braced function definitions ...
#' foo <- function(a, b, c) pkgpins::call_to_name()
#' foo(~ 1)
#' foo(function(x){x})
#'
#' # ... to mute those warnings, set `warn_incomplete = FALSE`
#' foo <- function(a, b, c) pkgpins::call_to_name(warn_incomplete = FALSE)
#' foo(~ 1)
#' foo(function(x){x})}
call_to_name <- function(n_generations_back = 1L,
                         add_namespace = TRUE,
                         rm_blanks = TRUE,
                         sanitize = TRUE,
                         non_destructive = FALSE,
                         exclude_args = c("use_cache", "cache_lifespan"),
                         warn_incomplete = TRUE) {
  
  checkmate::assert_count(n_generations_back)
  checkmate::assert_flag(add_namespace)
  checkmate::assert_flag(rm_blanks)
  checkmate::assert_flag(sanitize)
  checkmate::assert_flag(non_destructive)
  checkmate::assert_character(exclude_args,
                              any.missing = FALSE,
                              null.ok = TRUE)
  
  parent_frame_nr <- sys.parent(n_generations_back)
  parent_frame <- sys.frame(parent_frame_nr)
  call <- match.call(definition = sys.function(parent_frame_nr),
                     call = sys.call(parent_frame_nr))
  fn_name <- as.character(as.list(call)[[1L]])
  args <- as.list(call[-1L])
  
  # add namespace
  ## extract it if provided in call
  if (length(fn_name) == 3L) {
    
    fn_namespace <- fn_name[2L]
    fn_name <- fn_name[3L]
    
    ## or otherwise determine it manually
  } else if (length(fn_name) == 1L) {
    
    fn_envs <- methods::findFunction(f = fn_name,
                                     where = parent_frame)
    
    ### reduce to the first visible version of the function and extract env and namespace name
    if (length(fn_envs)) {
      
      fn_namespace <-
        fn_envs %>%
        dplyr::first() %>%
        environmentName() %>%
        ### reduce to actual package _namespace_ (in contrast to _environment_, cf. https://stackoverflow.com/a/38872833/7196903)
        stringr::str_extract(pattern = "(?<=^package:).+")
      
    } else {
      fn_namespace <- NA_character_
    }
  } else {
    rlang::abort("Unknown situation detected: Call's function has a length of 2! Please debug...")
  }
  
  if (add_namespace && !is.na(fn_namespace)) {
    fn_name %<>% paste0(fn_namespace, dplyr::if_else(sanitize && !non_destructive, "-", "::"), .)
  }
  
  # add args
  if (!is.null(exclude_args)) {
    excl <- names(args) %in% exclude_args
    
    if (length(excl)) {
      args <- args[!excl]
    }
  }
  
  if (length(args) > 0L) {
    
    # evaluate the call's arguments in the calling environment
    result <-
      args %>%
      purrr::map(.f = eval,
                 envir = parent_frame) %>%
      expr_to_name(rm_blanks = rm_blanks,
                   sanitize = sanitize,
                   non_destructive = non_destructive,
                   warn_incomplete = warn_incomplete) %>%
      # add function name
      paste0(fn_name, dplyr::if_else(nchar(.) > 0L, "-", ""), .)
      
  } else {
    
    if (sanitize && !non_destructive) {
      fn_name %<>% fs::path_sanitize()
    }
    
    result <- fn_name
  }
  
  result
}

expr_to_name <- function(expr,
                         rm_enclosing_list = TRUE,
                         rm_blanks,
                         sanitize,
                         non_destructive,
                         warn_incomplete) {
  
  checkmate::assert_flag(rm_enclosing_list)
  checkmate::assert_flag(warn_incomplete)
  
  # convert to string
  # (under rather exotic circumstances this is destructive, see `?..deparseOpts`)
  deparse1(expr = expr,
           collapse = "",
           control = c("keepNA",
                       "keepInteger",
                       "niceNames",
                       "showAttributes",
                       "warnIncomplete"[warn_incomplete])) %>%
    # remove enclosing "list()"
    purrr::when(rm_enclosing_list && stringr::str_detect(string = .,
                                                         pattern = "^list\\(.*\\)$") ~
                  stringr::str_remove_all(string = .,
                                          pattern = "(^list\\(|\\)$)"),
                ~ .) %>%
    # replace double quotes around character arguments with single quotes to make them filesystem safe
    # (this is a potentially destructive conversion step, and unnecessary anyway when non_destructive)
    stringr::str_replace_all(pattern = dplyr::if_else(sanitize && !non_destructive,
                                                      '(^|[^\\\\])(")(.+?[^\\\\])(")',
                                                      "^$"),
                             replacement = "\\1'\\3'") %>%
    # remove blanks
    # (this is a potentially destructive conversion step)
    stringr::str_replace_all(pattern = dplyr::if_else(rm_blanks && !non_destructive,
                                                      "\\s+",
                                                      "^$"),
                             replacement = "") %>%
    # remove filesystem-unsafe chars
    # (this is a potentially destructive conversion step)
    purrr::when(sanitize && !non_destructive ~ fs::path_sanitize(.),
                ~ .)
}

# these are necessary for testing the `add_namespace` argument
test_call_to_name <- function(...) call_to_name()
test_call_to_name_no_ns <- function(...) call_to_name(add_namespace = FALSE)
```

# `with_cache`

TODO:

-   Use `pal::check_dots_named()` once it has matured.

-   Provide an even shorter way, like

    ``` {.r}
    cachely <- function(.fn,
                        ...,
                        .use_cache = TRUE,
                        .cache_lifespan = "1 day",
                        .id = call_to_hash(), # this might not work; alternatively default to `NULL` and use `call_to_hash()` internally
                        .pkg) {

      rlang::new_function() # TODO
    }
    ```

    which returns a function, similar to `purrr::safely()` 🥳

    Then change `with_cache()` to cache an expression? does caching an expr even make sense for pkgpins? I guess not... -\> then deprecate `with_cache()`
    instead!

    It probably makes sense to thoroughly read the chapter [Function factories](https://adv-r.hadley.nz/function-factories.html) of *Advanced R* first. 🤓

```{r}
#' Cache a function call
#'
#' This is a convenience wrapper to cache the result of calling a function `.fn(...)`.
#'
#' @param .fn A function or formula.
#'
#'   If a **function**, it is used as is.
#'
#'   If a **formula**, e.g. `~ .x + 2`, it is converted to a function with up to two arguments: `.x` (single argument) or `.x` and `.y` (two arguments). The
#'   `.` placeholder can be used instead of `.x`. This allows you to create very compact anonymous functions (lambdas) with up to two inputs. See
#'   [rlang::as_function()] for details.
#' @param ... Additional arguments passed on to `.fn`.
#' @param .use_cache `r pkgsnip::param_label("use_cache")`
#' @param .cache_lifespan `r pkgsnip::param_label("cache_lifespan")`
#' @param .id The pin name uniquely identifying `x` in the `.pkg`'s user-cache pins board. A character scalar. An already existing pin named `.id` will be
#'   silently overwritten.
#' @param .pkg Package name. A character scalar.
#'
#' @return The result of calling `.fn(...)`, from cache if `.use_cache = TRUE` and a cached result exists that hasn't exceeded `.cache_lifespan`.
#' @export
#'
#' @examples
#' \donttest{
#' # if the fn below would be part of a real package, we could instead define `this_pkg`
#' # globally using `this_pkg <- utils::packageName()`
#' this_pkg <- "not.a.real.pkg"
#' 
#' # let's define a fn that returns R pkg sys deps from cache
#' pkg_sys_deps <- function(pkg,
#'                          use_cache = TRUE,
#'                          cache_lifespan = "6h") {
#'   pkgpins::with_cache(
#'     .fn = ~ purrr::flatten(jsonlite::fromJSON(txt = paste0("https://sysreqs.r-hub.io/pkg/", .x),
#'                                               simplifyVector = FALSE)),
#'     pkg,
#'     .use_cache = use_cache,
#'     .cache_lifespan = cache_lifespan,
#'     .pkg = this_pkg
#'   )
#' }
#' # now get the sys deps for git2r for the first time (populating the cache)
#' pkg_sys_deps("git2r")}
#' \dontrun{
#' # for the `cache_lifespan` (we've set a default of 6h), the cached result will be returned
#' # (as long as `use_cache = TRUE`):
#' bench::mark("with cache" = pkg_sys_deps("git2r"),
#'             "without cache" = pkg_sys_deps("git2r", use_cache = FALSE),
#'             iterations = 10,
#'             relative = TRUE)}
with_cache <- function(.fn,
                       ...,
                       .use_cache = TRUE,
                       .cache_lifespan = "1 day",
                       .id = call_to_hash(n_generations_back = 2L),
                       .pkg) {
  
  checkmate::assert_flag(.use_cache)
  .fn <- rlang::as_function(.fn,
                            env = parent.frame())
  fetch <- TRUE
  
  if (.use_cache) {
    
    result <- get_obj(id = .id,
                      max_age = .cache_lifespan,
                      pkg = .pkg)
    
    fetch <- is.null(result)
    
  }
  
  if (fetch) {
    result <- .fn(...)
  }
  
  if (.use_cache && fetch) {
    
    cache_obj(result,
              id = .id,
              pkg = .pkg)
  }
  
  result
}
```
