---
editor_options:
  chunk_output_type: console
---

# NOTES

Avoiding the pins package would have the following

-   advantages:

    -   Less dependencies.
    -   Less maintenance burden (in case of further pins API changes).
    -   Slightly better performance (although quite irrelevant since (de)serialization is by far the most expensive step which must be performed anyways and is
        already optimized).

-   disadvantages:

    -   We'd lose the possibility of easily expanding the current functionality (local boards) to remote caching (e.g. Amazon S3 boards).
    -   pins are some kind of established standard we'd lose.

# INTERNAL

## Avoid `R CMD check` notes about undefined global objects used in magrittr pipes

cf. <https://github.com/tidyverse/magrittr/issues/29#issuecomment-74313262>

```{r}
utils::globalVariables(names = c(".",
                                 "created",
                                 "file_size",
                                 "meta",
                                 "name",
                                 "pins_api_version",
                                 "pin_hash"))
```

## Functions

### `as_duration`

```{r}
as_duration <- function(max_age) {
  
  max_age_num <- lubridate::as.duration(max_age)
  
  # ensure `max_age` is valid
  if (is.na(max_age_num)) {
    cli::cli_abort(paste0("{.arg max_age} is set to {.val {max_age}} which is {.emph not} interpretable as a valid lubridate duration (using {.fun ",
                          "lubridate::as.duration})."))
  }
  
  max_age_num
}
```

### `ls_board_paths`

```{r}
ls_board_paths <- function(pkg) {
  
  tools::R_user_dir(package = "pkgpins",
                    which = "cache") %>%
    fs::dir_ls(type = "dir",
               regexp = glue::glue("/{pkg}(-.+)?$"))
}
```

# EXPORTED

## High-level functions

### `with_cache`

NOTES:

-   tidyverse devs [discourage](https://github.com/tidyverse/magrittr/blob/master/NEWS.md#incorrect-call-stack-introspection) the use of `sys.parent()`,
    `sys.frame()` and friends and recommend to only rely on `parent.frame()` since it is the only base R function that allows to query the *call stack* -- and
    thus also works when R code is called from *non-inspectable* frames. See `?rlang::stack` for more information on the *call* vs. the *context stack* in R.

```{r}
#' Cache the result of an expression
#'
#' One-stop solution to add caching to any R expression, for example from within a function. See the examples.
#'
#' `expr` is evaluated in the environment that `with_cache()` is called from.
#'
#' See [hash_fn_call()] for details about how the pin name is constructed that uniquely identifies `expr` in the `pkg`'s user-cache pins board.
#'
#' @inheritParams board
#' @param expr Expression to cache.
#' @param pkg_versioned Whether or not to make the caching dependent on the version number of `pkg`. If `FALSE`, caching is agnostic about `pkg`'s version
#'   number. Otherwise, a separate user-cache pins board is created each time `pkg`'s version number changes (e.g. after an upgrade), ensuring to never return
#'   cached results from a different (old) package version, irrespective of `max_cache_age`.
#' @param from_fn Name of the function that `expr` is cached from, i.e. the name of the function that `with_cache()` is called from. A character scalar.
#' @param ... Arguments received by `from_fn` on which the caching should depend. This is fundamental to determine whether `expr` was already cached or not. The
#'   arguments must be specified _unnamed_ (see examples). `r pkgsnip::param_label("dyn_dots_support")`
#' @param use_cache `r pkgsnip::param_label("use_cache")`
#' @param max_cache_age `r pkgsnip::param_label("max_cache_age")` 
#'
#' @return The result of evaluating `expr`, from cache if `use_cache = TRUE` and a cached result exists that hasn't exceeded `max_cache_age`.
#' @family high_lvl
#' @export
#'
#' @examples
#' # if the fn below would be part of a real package, we could instead define `this_pkg` globally
#' # using `this_pkg <- utils::packageName()`; instead, we now cache to pkgpins's cache (which
#' # itself never uses the cache)
#' this_pkg <- "pkgpins"
#' 
#' # let's define a fn that returns R pkg sys deps from cache
#' pkg_sys_deps <- function(pkg,
#'                          use_cache = TRUE,
#'                          max_cache_age = "6h") {
#'   pkgpins::with_cache(
#'     expr = purrr::list_flatten(jsonlite::fromJSON(txt = paste0("https://sysreqs.r-hub.io/pkg/",
#'                                                                pkg),
#'                                                   simplifyVector = FALSE)),
#'     pkg = this_pkg,
#'     from_fn = "pkg_sys_deps",
#'     pkg,
#'     use_cache = use_cache,
#'     max_cache_age = max_cache_age
#'   )
#' }
#' 
#' # now get the sys deps for git2r for the first time (populating the cache)
#' pkg_sys_deps("git2r")
#' 
#' \dontrun{
#' # for the `max_cache_age` (we've set a default of 6h), the cached result will be returned
#' # (as long as `use_cache = TRUE`):
#' bench::mark("with cache" = pkg_sys_deps("git2r"),
#'             "without cache" = pkg_sys_deps("git2r", use_cache = FALSE),
#'             iterations = 10,
#'             relative = TRUE)}
#' 
#' # purge cache from the above example
#' pkgpins::board(pkg = "pkgpins") |> pkgpins::purge_cache()
with_cache <- function(expr,
                       pkg,
                       from_fn,
                       ...,
                       pkg_versioned = TRUE,
                       use_cache = TRUE,
                       max_cache_age = "1 day") {
  
  checkmate::assert_flag(use_cache)
  
  fetch <- TRUE
  
  if (use_cache) {
    
    board <- board(pkg = pkg,
                   pkg_versioned = pkg_versioned)
    id <- hash_fn_call(from_fn = from_fn,
                       ...)
    
    # NOTE: we can't use `get_obj()` here because in case of return value `NULL` we wouldn't know whether it means there's no cached result or the cached
    #       result is just `NULL`
    if (is_cached(board = board,
                  id = id,
                  max_age = max_cache_age)) {
      
      result <- pins::pin_read(board = board,
                               name = id)
      fetch <- FALSE
    }
  }
  
  if (fetch) {
    result <- rlang::eval_bare(expr = expr,
                               env = parent.frame(n = 2L))
  }
  
  if (use_cache && fetch) {
    cache_obj(board = board,
              x = result,
              id = id)
  }
  
  result
}
```

### !`cachely`

EXPERIMENTAL; doesn't work as supposed (yet)!

TODO:

-   Figure out how to properly pass on `...` to `fn()`; Currently only works with lambda fns, not with "normal" non-lambda fns:

    ``` r
    sleepy <- function(x) { Sys.sleep(x); x }

    sleepless <- pkgpins::cachely(.pkg = "pkgpins",
                                  .fn_name = "sleepless",
                                  .fn = sleepy,
                                  .max_cache_age = "1 year")

    sleepless(1)                
    sleepless(1)
    ```

-   It probably makes sense to thoroughly read the chapter [Function factories](https://adv-r.hadley.nz/function-factories.html) of *Advanced R* at some point
    in order to actually understand what we're doing here... 🤪

```{r, purl = FALSE}
#' Add caching to a function
#' 
#' Extends a function `.fn` by caching. Note that the caching is based on *all* arguments of `.fn`. Use [with_cache()] if you need more control.
#'
#' @param .pkg Package name to which `.fn` belongs. A character scalar.
#' @param .fn_name Name of the newly created function, i.e. the name for the function that is returned by `cachely()`. A character scalar.
#' @param .fn A function or formula.
#'
#'   If a **function**, it is used as is.
#'
#'   If a **formula**, e.g. `~ .x + 2`, it is converted to a function with up to two arguments: `.x` (single argument) or `.x` and `.y` (two arguments). The
#'   `.` placeholder can be used instead of `.x`. This allows you to create very compact anonymous functions (lambdas) with up to two inputs. See
#'   [rlang::as_function()] for details.
#' @param ... Additional arguments passed on to `.fn`.
#' @param .use_cache `r pkgsnip::param_label("use_cache")`
#' @param .max_cache_age `r pkgsnip::param_label("max_cache_age")`
#'
#' @return A modified version of `.fn` that uses caching.
#' @export
#'
#' @examples
#' # if the fn below would be part of a real package, we could instead define `this_pkg` globally
#' # using `this_pkg <- utils::packageName()`; instead, we now cache to pkgpins's cache (which
#' # itself never uses the cache)
#' this_pkg <- "pkgpins"
#'
#' # create a sleep function that caches sleeping (if only humans could do the same!)
#' sleepless <- pkgpins::cachely(.pkg = this_pkg,
#'                               .fn_name = "sleepless",
#'                               .fn = ~ { Sys.sleep(.x); .x },
#'                               .max_cache_age = "1 year")
#'
#' # populate the cache...
#' sleepless(0.5)
#' sleepless(1)
#' 
#' # ... and never sleep the same amount of time again (for the next year)
#' sleepless(0.5)
#' sleepless(1)
#' 
#' # purge cache from the above example
#' pkgpins::board(pkg = "pkgpins") |> pkgpins::purge_cache()
cachely <- function(.pkg,
                    .fn_name,
                    .fn,
                    ...,
                    .use_cache = TRUE,
                    .max_cache_age = "1 day") {
  
  fn <- rlang::as_function(.fn,
                           env = parent.frame())
  
  rlang::new_function(args = rlang::fn_fmls(fn),
                      body = quote(expr = with_cache(expr = do.call(what = fn, # an alternative would be rlang::exec(), JFYI
                                                                    args = rlang::fn_fmls_syms(fn)),
                                                     pkg = .pkg,
                                                     from_fn = .fn_name,
                                                     ...,
                                                     use_cache = .use_cache,
                                                     max_cache_age = .max_cache_age)))
}
```

## Low-level functions

### Manage package cache

#### DESCRIPTION

Functions to manage package user-cache pins board(s).

#### `board`

```{r}
#' Get a package's user-cache pins board
#'
#' Returns a `pkg`'s user-cache pins board. The board is automatically created if it doesn't already exist.
#'
#' @param pkg Package name. A character scalar.
#' @param pkg_versioned Whether or not to make the board name dependent on `pkg`'s version number. If `FALSE`, the board is agnostic about `pkg`'s version
#'   number. Otherwise, a separate board is created for each `pkg` version number (e.g. after an upgrade).
#'
#' @return The user-cache pins board belonging to `pkg` (and its version number if `pkg_versioned = TRUE`). An object of class
#'   [`pins_board_folder`][pins::board_folder].
#' @family pkg_cache_mgmt
#' @export
board <- function(pkg,
                  pkg_versioned = TRUE) {
  
  checkmate::assert_string(pkg)
  checkmate::assert_flag(pkg_versioned)
  
  if (pkg_versioned) {
    
    pkg %<>% paste(utils::packageVersion(pkg = pkg),
                   sep = "-")
  }
  
  tools::R_user_dir(package = "pkgpins",
                    which = "cache") %>%
    fs::path(pkg) %>%
    pins::board_folder(versioned = FALSE)
}
```

#### `path_cache`

```{r}
#' Get a package's user-cache pins board path
#'
#' Returns the filesystem path to the `pkg`'s user-cache pins board. Note that this path depends on the operating system this function is called from.
#' 
#' It shouldn't be necessary to rely on this function for the tasks this package is intended to perform, though.
#'
#' @param board [Package's user-cache pins board][board()].
#'
#' @return `r pkgsnip::return_label("path")`
#' @family pkg_cache_mgmt
#' @export
path_cache <- function(board) {
  
  checkmate::assert_class(board,
                          classes = "pins_board_folder")
  board$path
}
```

#### `ls_cache`

```{r}
#' List all objects in a package's user-cache pins board
#'
#' Lists all objects stored in a `pkg`'s user-cache pins board.
#'
#' @inheritParams path_cache
#'
#' @return A [tibble][tibble::tbl_df] containing the columns `id`, `date_time_cached`, `file_size` and `pins_api_version`.
#' @family pkg_cache_mgmt
#' @export
ls_cache <- function(board) {
  
  checkmate::assert_class(board,
                          classes = "pins_board_folder")
  
  pins::pin_search(board = board) %>%
    dplyr::mutate(pins_api_version = meta %>% purrr::map_dbl(purrr::chuck, "api_version")) %>%
    dplyr::select(id = name,
                  date_time_cached = created,
                  file_size,
                  pins_api_version)
}
```

#### `clear_cache`

```{r}
#' Clear a package's user-cache pins board
#'
#' Deletes all objects from a package's user-cache pins board that exceed a certain `max_age`. If `board` is `pkg_versioned`, additionally deletes all
#' user-cache pins boards belonging to versions of the package other than the currently installed one.
#'
#' This function could be called on package load/unload, for example.
#'
#' @inheritParams path_cache
#' @param max_age Age above which cached objects will be deleted. A valid [lubridate duration][lubridate::as.duration]. Defaults to 1 day (24 hours).
#'
#' @return `board`, invisibly.
#' @family pkg_cache_mgmt
#' @export
#'
#' @examples
#' \dontrun{
#' # delete all cached results that are older than 7 days at once on package load:
#' .onLoad <- function(libname, pkgname) {
#'   pkgpins::clear_cache(board = pkgpins::board(pkg = pkgname),
#'                        max_age = "7 days")
#' }}
clear_cache <- function(board,
                        max_age = "1 day") {
  
  # delete boards from different pkg versions
  path_cache <- fs::path_real(path_cache(board))
  board_name <- fs::path_file(path_cache)
  incl_pkg_version <- stringr::str_detect(board_name, "-")
  
  if (incl_pkg_version) {
    
    board_name %>%
      stringr::str_extract("^[^-]+") %>%
      ls_board_paths() %>%
      setdiff(y = path_cache) %>%
      purrr::walk(fs::dir_delete)
  }
  
  # delete results that exceed max age
  board %>%
    pins::pin_search() %>%
    dplyr::filter(lubridate::now(tzone = "UTC") - created > as_duration(!!max_age)) %$%
    name %>%
    pins::pin_delete(board = board)
}
```

#### `purge_cache`

```{r}
#' Purge a package's user-cache pins board
#'
#' Deletes *all* objects from a package's user-cache pins board. All boards belonging to the same package as `board` are deleted, too.
#'
#' @inheritParams path_cache
#'
#' @family pkg_cache_mgmt
#' @export
purge_cache <- function(board) {
  
 path_cache(board) %>%
    fs::path_file() %>%
    stringr::str_extract("^[^-]+") %>%
    ls_board_paths() %>%
    purrr::walk(fs::dir_delete)
}
```

#### `purge_caches`

```{r}
#' Purge all package user-cache pins boards
#'
#' Deletes the user-cache pins boards of *all* packages.
#'
#' @return The deleted filesystem [paths][fs::fs_path], invisibly. Of length 0 if no package user-cache pins boards did exist.
#' @family pkg_cache_mgmt
#' @export
purge_caches <- function() {
  
  fs::dir_delete(path = tools::R_user_dir(package = "pkgpins",
                                          which = "cache"))
}
```

### Handle objects

#### DESCRIPTION

Functions to cache/retrieve/delete results of a function call.

#### `hash_fn_call`

```{r}
#' Hash a function call
#'
#' Creates a string that uniquely identifies a function call by the function's name and a hash of the specified arguments.
#' 
#' `r foo <- function(a) pkgpins::hash_fn_call("foo", a); NULL`
#' 
#' This function does evaluate all arguments in `...`. I.e. the function call `mypkg::foo(a = my_var)` will be cached as `r pal::wrap_chr(foo(100))` if
#' `my_var`'s value is `100`, whereas it will become `r pal::wrap_chr(foo(101))` if `my_var`'s value is `101`. See examples below.
#'
#' @param from_fn Name of the function from which `hash_fn_call()` is called. A character scalar.
#' @param ... Arguments `from_fn` was called with. Any arguments omitted here won't be taken into account when generating the hash.
#'
#' @return A character scalar.
#' @family obj_handling
#' @export
#'
#' @examples
#' foo <- function(a, b = "default") pkgpins::hash_fn_call("foo", a, b)
#' 
#' foo("bar")
#' a <- "bar"
#' foo(a)
#' a <- "barbie"
#' foo(a)
#' a |> foo()
#' a |> foo(b = "default")
#' 
#' # you can also create a hash that is based on a subset of all function arguments
#' foo <- function(a, b = "default") pkgpins::hash_fn_call("foo", b)
#' 
#' foo("bar")
#' foo("barrr")
#' foo(b = "bar")
hash_fn_call <- function(from_fn,
                         ...) {
  
  checkmate::assert_string(from_fn)
  rlang::check_dots_unnamed()
  
  rlang::dots_list(...,
                   .homonyms = "error",
                   .ignore_empty = "trailing",
                   .preserve_empty = FALSE,
                   .check_assign = TRUE) %>%
    rlang::hash() %>%
    paste(from_fn, .,
          sep = "-")
}
```

#### `is_cached`

```{r}
#' Test whether an object exists in a package's user-cache pins board
#'
#' Returns `TRUE` if the object is present in the `pkg`'s user-cache pins board and hasn't exceeded `max_age`, otherwise `FALSE`.
#'
#' @inheritParams path_cache
#' @param id Pin name uniquely identifying the object to be checked in the `pkg`'s user-cache pins board. A character scalar.
#' @param max_age Maximum age the cached object is allowed to have. A valid [lubridate duration][lubridate::as.duration]. Defaults to 1 day (24 hours).
#'
#' @return A character scalar, or `NULL` if no cached object exists that hasn't exceeded `max_age`.
#' @family obj_handling
#' @export
is_cached <- function(board,
                      id,
                      max_age = "1 day") {
  
  checkmate::assert_string(id)
  checkmate::assert_class(board,
                          classes = "pins_board_folder")
  
  cache <- pins::pin_search(board = board)
  
  if (nrow(cache)) {
    
    cache %<>% dplyr::filter(name == id & lubridate::now(tzone = "UTC") - created <= as_duration(!!max_age))
    
    if (nrow(cache) > 1L) {
      cli::cli_abort(paste0("Multiple pins with {.arg id} {.val {id}} found for the {.val {fs::path_file(board$path)}} board. This should not happen since ",
                            "versioning is disabled for pkgpins boards... \U1F41E"))
    }
  }
  
  nrow(cache) > 0L
}
```

#### `cache_obj`

TODO:

-   [ ] Systematically assess and ideally improve get performance.

    A first benchmark shows the pins overhead is pretty low and almost all delay caused by decompression:

    ``` r
    bench::mark(indirect = swissevote::read_raw_data(canton = "Geneva",
                                                     ballot_date = "2018-06-10"),
                direct = readRDS("/home/salim/.cache/pins/pkg-cache-swissevote/swissevote-read_raw_data-canton='Geneva',ballot_date='2018-06-10'/data.rds"),
                check = FALSE,
                iterations = 10L)
    ```

NOTES:

-   We don't rely on `pins::pin_write()` because it

    1.  has quite a lot of overhead for our purpose, e.g. it always first stores the object in system's temp dir and afterwards copies it to the actual board
        and deletes the temp copy. And it does quite a lot of other processing we don't need.
    2.  doesn't allow to alter the defaults of `qs::qsave()`.
    3.  always displays an annoying message like `Creating new version '20211106T044834Z-dcd18'` which cannot be disabled.

```{r}
#' Cache an object to a package's user-cache pins board
#'
#' Stores an object in `pkg`'s user-cache pins board, i.e. caches it to the filesystem.
#'
#' Note that `cache_obj()` will always overwrite an already existing cached object of the same `id`. See [hash_fn_call()] for a convenient way to create an `id`
#' that uniquely identifies a function call. Or just use [with_cache()] that internally relies on the former.
#'
#' Note that reading in the cached result from the user-cache pins board (i.e. from the filesystem) might produce a noticeable delay depending on the size of
#' the cached object. Therefore, it's only recommended to cache results that take a considerable amount of time to recompute. To avoid the overhead of
#' re-reading a cached result when accessing it multiple times, you can always assign it to an R variable to benefit from direct storage in memory.
#'
#' @inheritParams path_cache
#' @param x Object to be cached.
#' @param id Pin name uniquely identifying `x` in the `pkg`'s user-cache pins board. A character scalar which is safe to use in paths of common file systems.
#'   Necessary to retrieve `x` again using [get_obj()]. An already existing pin named `id` will be silently overwritten.
#' @param qs_preset The serialization algorithm preset to use. See [qs::qsave()] (section *Presets*) for details.
#'
#' @return `x`, invisibly.
#' @family obj_handling
#' @export
#'
#' @examples
#' # if the fn below would be part of a real package, we could instead define `this_pkg` globally
#' # using `this_pkg <- utils::packageName()`; instead, we now cache to pkgpins's cache (which
#' # itself never uses the cache)
#' board <- pkgpins::board(pkg = "pkgpins")
#' 
#' # let's define a fn that returns R pkg sys deps from cache
#' pkg_sys_deps <- function(pkg,
#'                          use_cache = TRUE,
#'                          max_cache_age = "6h") {
#'   fetch <- TRUE
#'
#'   if (use_cache) {
#'     pin_name <- pkgpins::hash_fn_call(from_fn = "pkg_sys_deps",
#'                                       pkg)
#'     result <- pkgpins::get_obj(board = board,
#'                                id = pin_name,
#'                                max_age = max_cache_age)
#'     fetch <- is.null(result)
#'   }
#'   
#'   if (fetch) {
#'     result <-
#'       jsonlite::fromJSON(txt = paste0("https://sysreqs.r-hub.io/pkg/", pkg),
#'                          simplifyVector = FALSE) |>
#'       purrr::list_flatten()
#'   }
#'  
#'   if (use_cache && fetch) {
#'     pkgpins::cache_obj(board = board,
#'                        x = result,
#'                        id = pin_name)
#'   }
#'
#'   result
#' }
#'
#' # now get the sys deps for git2r for the first time (populating the cache)
#' pkg_sys_deps("git2r")
#'
#' \dontrun{
#' # for the `max_cache_age` (we've set a default of 6h), the cached result will be returned
#' # (as long as `use_cache = TRUE`):
#' bench::mark("with cache" = pkg_sys_deps("git2r"),
#'             "without cache" = pkg_sys_deps("git2r", use_cache = FALSE),
#'             iterations = 10,
#'             relative = TRUE)}
#' 
#' # purge cache from the above example
#' pkgpins::purge_cache(board = board)
cache_obj <- function(board,
                      x,
                      id,
                      qs_preset = c("fast", "balanced", "high", "archive")) {
  
  checkmate::assert_class(board,
                          classes = "pins_board_folder")
  checkmate::assert_string(id,
                           pattern = "^[^/\\\\]+$")
  qs_preset <- rlang::arg_match(qs_preset)
  
  # ensure `id` is safe to use as fs path
  if (id != fs::path_sanitize(id)) {
    cli::cli_abort("{.arg id} contains characters which are not safe to use in common file system paths, cf. {.code ?fs::path_sanitize}")
  }
  
  # serialize obj
  date_time_created <- format(Sys.time(),
                              "%Y%m%dT%H%M%SZ",
                              tz = "UTC")
  path_dir <-
    path_cache(board) %>%
    fs::path(id, glue::glue("{date_time_created}-00000")) %>%
    fs::dir_create()
  
  path_file <- "cache.qs"
  path <- fs::path(path_dir, path_file)
  
  qs::qsave(x = x,
            file = path,
            preset = qs_preset,
            check_hash = TRUE)
  
  # write pin metadata
  yaml::write_yaml(x = list(file = path_file,
                            file_size = as.integer(fs::file_size(path)),
                            # pin hash is omitted since a) not sensible for our purpose and b) `qs::qsave()` stores an integrity hash in file anyways
                            pin_hash = NULL,
                            type = "qs",
                            title = id,
                            description = NULL,
                            created = date_time_created,
                            api_version = 1,
                            user = NULL),
                   file = fs::path(path_dir, "data.txt"))
}
```

#### `get_obj`

```{r}
#' Get a cached object from a package's user-cache pins board
#'
#' Retrieves a cached object from a package's user-cache pins board _if_ it is not older than `max_age`.
#'
#' @inheritParams is_cached
#' @param id Pin name uniquely identifying the object to be retrieved from the `pkg`'s user-cache pins board. A character scalar.
#'
#' @return The cached object if it is not older than `max_age`, otherwise `NULL`.
#' @family obj_handling
#' @export
get_obj <- function(board,
                    id,
                    max_age = "1 day") {
  
  if (is_cached(board = board,
                id = id,
                max_age = max_age)) {
    
    result <- pins::pin_read(board = board,
                             name = id)
  } else {
    result <- NULL
  }
  
  result
}
```

#### `rm_obj`

```{r}
#' Delete a cached object from a package's user-cache pins board
#'
#' Removes a cached object from a package's user-cache pins board.
#'
#' Note that it normally won't be necessary to delete a cached object using this function because [cache_obj()] will always overwrite a possibly existing object
#' in the cache with the same `id`. If you want to ensure that no "data corpses" are left behind from using [cache_obj()], consider [clearing][clear_cache] or
#' even [purging][purge_cache] the whole package user-cache pins board at once.
#'
#' @inheritParams path_cache
#' @param id Pin name uniquely identifying the object to be deleted from the `pkg`'s user-cache pins board. A character scalar.
#'
#' @return `id`, invisibly.
#' @family obj_handling
#' @export
rm_obj <- function(board,
                   id) {
  
  checkmate::assert_class(board,
                          classes = "pins_board_folder")
  checkmate::assert_string(id)
  
  pins::pin_delete(board = board,
                   names = id)
  invisible(id)
}
```
