---
output: pal::gitlab_document
---

# `r paste0(pal::desc_value("Package"), ": ", pal::desc_value("Title"))`

`r pal::desc_value("Description")`

## Predefined parameter labels

There are two predefined parameter labels available in [pkgsnippets](https://gitlab.com/salim_b/r/pkgs/pkgsnippets) which fit typical use cases of this
package. They are intended to be used in `@param` [roxygen2 tags](https://roxygen2.r-lib.org/articles/rd.html#functions)[^v710] as follows:

```r
#' @param cache_lifespan `r '\x60r pkgsnippets::param_label("cache_lifespan")\x60'`
#' @param use_cache `r '\x60r pkgsnippets::param_label("use_cache")\x60'`
```

The above inline R code will eventually result in this:

```r
#' @param cache_lifespan `r pkgsnippets::param_label("cache_lifespan")`
#' @param use_cache `r pkgsnippets::param_label("use_cache")`
```


[^v710]: Support for dynamic inline R code was introduced in [roxygen2 7.1.0](https://www.tidyverse.org/blog/2020/03/roxygen2-7-1-0/).


## Installation
```{r, install-snippet-dev, child = pkgsnippets::snippet_path("installation-notice_dev-version_gitlab.Rmd")}
```

## Development

### R Markdown format
```{r, rmd-pkg-snippet, child = pkgsnippets::snippet_path("rmd-package-notice.Rmd")}
```

### Coding style
```{r, coding-style-snippet, child = pkgsnippets::snippet_path("coding-style-notice.Rmd")}
```

## See also

- R packages that provide a [memoization](http://en.wikipedia.org/wiki/Memoization) infrastructure. Memoization is suited best for caching strict functional
  programming results, i.e. caching functions that always return the same result with the same arguments – something that's often not the case for functions
  accessing external APIs.

    There are at least two actively developed memoization packages:
  
    - The Tidyverse-style [**memoise**](https://github.com/r-lib/memoise) package.
    - The [**R.cache**](https://github.com/HenrikBengtsson/R.cache) package.
