---
output: pal::gitlab_document
---

# `r paste0(pal::desc_value("Package"), ": ", pal::desc_value("Title"))`

`r pal::desc_value("Description")`

## Installation
```{r, install-snippet-dev, child = pkgsnippets::file("installation-notice_dev-version_gitlab.Rmd")}
```

## Development

### Literate Programming
```{r, literate-programming-snippet, child = pkgsnippets::file("literate-programming-notice.Rmd")}
```

### Coding Style
```{r, coding-style-snippet, child = pkgsnippets::file("coding-style-notice.Rmd")}
```

## See also

- R packages that provide a [memoization](http://en.wikipedia.org/wiki/Memoization) infrastructure. Memoization is suited best for caching strict functional programming results, i.e. caching functions that always return the same result with the same arguments – something that's often not the case for functions accessing external APIs.

    There are at least two actively developed memoization packages:
  
    - The Tidyverse-style [**memoise**](https://github.com/r-lib/memoise) package.
    - The [**R.cache**](https://github.com/HenrikBengtsson/R.cache) package.
