---
output: pal::gitlab_document
---

# `r paste0(pal::desc_value("Package"), ": ", pal::desc_value("Title"))`

`r pal::desc_value("Description") %>% stringr::str_replace(" (pins)( package) ", " [\\1](https://pins.rstudio.com/)\\2 ")`

## Predefined parameter labels

There are two predefined parameter labels available in [pkgsnip](https://gitlab.com/salim_b/r/pkgs/pkgsnip) which fit typical use cases of this package. They
are intended to be used in `@param` [roxygen2 tags](https://roxygen2.r-lib.org/articles/rd.html#functions)[^1] as follows:

[^1]: Support for dynamic inline R code was introduced in [roxygen2 7.1.0](https://www.tidyverse.org/blog/2020/03/roxygen2-7-1-0/).

``` {.r}
#' @param cache_lifespan `r '\x60r pkgsnip::param_label("cache_lifespan")\x60'`
#' @param use_cache `r '\x60r pkgsnip::param_label("use_cache")\x60'`
```

The above inline R code will eventually result in this:

``` {.r}
#' @param cache_lifespan `r pkgsnip::param_label("cache_lifespan")`
#' @param use_cache `r pkgsnip::param_label("use_cache")`
```

## Installation

```{r, install-snippet-dev, child = pkgsnip::snip_path("installation-notice_dev-version_gitlab.Rmd")}
```

## Development

### R Markdown format

```{r, rmd-pkg-snippet, child = pkgsnip::snip_path("rmd-package-notice.Rmd")}
```

### Coding style

```{r, coding-style-snippet, child = pkgsnip::snip_path("coding-style-notice.Rmd")}
```

## See also

-   R packages that provide a [memoization](http://en.wikipedia.org/wiki/Memoization) infrastructure. Memoization is suited best for caching [purely functional
    programming](https://en.wikipedia.org/wiki/Purely_functional_programming) results, i.e. caching functions that *always* return the same result for the same
    arguments (complete statelessness) -- something that's often not the case for functions accessing external APIs.

    There are at least two actively developed memoization packages:

    -   The Tidyverse-style [**memoise**](https://github.com/r-lib/memoise) package.
    -   The [**R.cache**](https://github.com/HenrikBengtsson/R.cache) package.

-   The R package [**storr**](https://richfitz.github.io/storr/) that acts as a simple object cacher supporting various [storage back
    ends](https://richfitz.github.io/storr/articles/storr.html#supported-backends). Notable is the [**thor**](https://richfitz.github.io/thor/index.html) back
    end that combines in-memory-mapping via [LMDB](https://symas.com/lmdb/) with on-disk caching.
